\section{Mission Statement}\label{sec:mission-statement}
In the landscape of scientific computation, the types of computation are traditionally divided into two broad categories: numerical and symbolic.
While numerical methods have long been at the forefront of computational science, symbolic computation remains essential for the theoretical underpinnings of many scientific domains.
DeduKt is designed to provide a comprehensive solution for symbolic computation, while maintaining a seamless integration with numerical methods.
This duality is crucial as many scientific workflows rely on the interplay between abstract, symbolic reasoning and empirical, numerical analysis.

The fundamental premise of DeduKt is to empower users to compute and manipulate mathematical expressions within their correct contextual framework.
Unlike conventional tools that focus solely on the evaluation of expressions, DeduKt emphasizes the need for intelligent reasoning throughout the computational process.
This means not only evaluating equations, but also offering insights, suggestions, and paths for exploration that can guide users through their computations.
By understanding the broader context of the problem, DeduKt allows users to reason, experiment, and iterate more effectively.

Moreover, modern scientific workflows are increasingly data-driven.
While theoretical models provide critical insights, the need to analyze and interpret data from experiments is equally important.
DeduKt aims to be a bridge between theory and experiment, enabling users to seamlessly transition from mathematical derivations to real-world data analysis.
The ability to integrate symbolic computation with experimental data handling ensures that DeduKt remains versatile and functional in a wide range of research scenarios.

The goal of DeduKt is to provide the following key capabilities:

\begin{itemize}
    \item An extensible and modular framework for mathematical computation and symbolic manipulation, designed to easily accommodate new mathematical structures, algorithms, and evaluation methods as they evolve in the field.
    \item A powerful toolkit for data manipulation, processing, and visualization, enabling users to analyze experimental data alongside their symbolic models.
    This toolkit will support a range of formats and provide intuitive interfaces for data exploration.
    \item Intelligent reasoning systems that not only ensure the correctness of computations but also assist in the development of rigorous mathematical proofs, theorem generation, and symbolic simplifications.
    This will empower users to conduct research at the forefront of mathematical exploration.
    \item A commitment to being a free, open-source software project, fostering a vibrant community of contributors, educators, and researchers.
    This ensures that DeduKt remains accessible, adaptable, and continuously improved by the collective efforts of its user base.
    \item Complementary integration with ISK's Numerical Foundation Library (Kompute), providing a unified computational environment for both numerical and symbolic tasks.
    This synergy will allow users to approach problems from both a theoretical and experimental perspective without needing to switch tools.
    \item A minimalistic core design focused on efficiency, performance, and flexibility, while offering users the ability to define their own symbolic computation methods.
    The system will prioritize a clean, user-friendly interface, even as it supports complex and customizable use cases.
    \item High performance and scalability, ensuring that DeduKt can handle large-scale computations and complex symbolic manipulations without sacrificing speed or responsiveness.
    This includes optimizations for both single-user applications and collaborative, distributed environments.
\end{itemize}
