\section{Non-Goals}\label{sec:non-goals}
While DeduKt is designed to be a powerful tool for symbolic computation and mathematical reasoning, there are several areas that are intentionally outside the current scope of the project.
These non-goals represent areas where DeduKt does not aim to provide functionality or where certain capabilities are deliberately excluded to maintain focus on its core mission.
It is important to note that the scope of DeduKt is subject to change as the project evolves, and if the mission statement shifts, these non-goals may be revisited or expanded.

The following are key aspects that are not within the current scope of the DeduKt project:

\begin{itemize}
    \item \textbf{Numerical Simulation and High-Performance Computing (HPC)}: While DeduKt integrates symbolic computation with numerical data analysis, it does not aim to provide comprehensive numerical simulation or high-performance computing features.
    For advanced numerical tasks like large-scale simulations or parallel processing of mathematical models, users are encouraged to rely on specialized numerical software like Kompute or other HPC tools.

    \item \textbf{Graphical User Interface (GUI)}: DeduKt is primarily focused on providing a powerful computational engine for symbolic reasoning.
    While the system may include some minimal user interfaces for basic interaction, DeduKt does not currently prioritize the development of a full-featured GUI.
    The emphasis remains on the core computational engine and command-line or script-based interfaces.

    \item \textbf{Advanced Machine Learning or AI Integration}: DeduKt is not intended to serve as a platform for advanced machine learning or artificial intelligence applications.
    While the software may allow users to integrate or manipulate data produced by machine learning algorithms, it does not include native support for training models, neural networks, or deep learning techniques.
    For AI-driven tasks, users should turn to specialized frameworks like TensorFlow or PyTorch.

    \item \textbf{General-Purpose Programming Language Features}: DeduKt is not designed to be a general-purpose programming language.
    Although it supports some user-defined symbolic computation and custom operations, it does not intend to compete with full-fledged programming languages like Python, Go, or Kotlin for broad software development tasks.
    DeduKt’s focus is on symbolic mathematics and mathematical reasoning, not on general software engineering.

    \item \textbf{Real-Time Collaboration Features}: While DeduKt may be used in a collaborative research setting, it does not currently offer features for real-time collaborative editing or communication.
    Users looking for collaborative environments should rely on other tools designed for shared workflows, such as Jupyter notebooks, or consider using DeduKt alongside version control systems like Git.

    \item \textbf{Specialized Visualization Tools for Complex Data Sets}: While DeduKt includes basic data manipulation and visualization tools for mathematical expressions, it does not aim to replace specialized data visualization libraries or platforms.
    Complex visualizations such as interactive 3D plots, real-time data streams, or extensive dashboard frameworks are beyond the scope of the project.
    For advanced visualization, users are encouraged to integrate DeduKt with tools like Matplotlib, Plotly, or specialized scientific visualization software.

    \item \textbf{Commercial or Enterprise Support}: DeduKt is an open-source software project, and as such, it does not provide official commercial or enterprise-grade support.
    While the community-driven approach fosters collaboration and assistance, users requiring enterprise-level guarantees, support contracts, or specific service-level agreements (SLAs) should seek professional services elsewhere.

    \item \textbf{Native Support for All Mathematical Fields}: Although DeduKt is designed to handle a wide range of symbolic mathematical tasks, it does not support every niche or specialized area of mathematics.
    Areas requiring highly specialized algorithms, such as advanced cryptography or domain-specific symbolic methods, may not be fully supported at the outset.
    However, the extensible nature of DeduKt allows users to implement their own methods for these areas.
\end{itemize}
