\section{Overview}\label{sec:overview}
In mathematics and the natural sciences, computers serve not only as powerful tools for simulations and numerical computation but also as essential systems for symbolic manipulation of mathematical expressions.
Despite the many existing Computer Algebra Systems (CAS) and simulation software available today, they tend to follow different philosophies and payment plans that reduces their capabilities and community.
DeduKt is created to address and solve these issues.

DeduKt is an open-source, community-driven system designed for computer algebra, simulation, and data manipulation.
It provides a dynamic and expressive language for modeling and defining mathematics, leveraging Kotlin, a modern, statically typed, general-purpose language, as the main language of development (Unless others specified) and having a library for symbolic computation inside of it.
Through its unique approach and the connection between DeduKt and Independent Society of Knowledge's Kompute library, DeduKt aims to become a unified software for reasoning, modeling and quantitative researches.

While numerous powerful software systems like Wolfram Mathematica, COMSOL, and SageMath dominate the computational landscape, they often suffer from limitations such as cost, complexity, and closed-source nature.
DeduKt stands as an open alternative, offering both the flexibility and extensibility needed for modern computational workflows.
It aims to break free from the constraints of proprietary software, ensuring that users have complete control over their computational environment while benefiting from the power and robustness of a community-driven open-source platform.

At its core, DeduKt is designed to be a hybrid tool that can be used both as a standalone software package and as a Kotlin library, enabling seamless integration into existing Kotlin-based workflows.
With Kompute, DeduKt's numerical computing counterpart, the system supports a wide range of applications—from symbolic computation to advanced simulation tasks—while maintaining a focus on performance, usability, and scalability.

As a community-driven project, DeduKt's future is shaped by the contributions and feedback of its users.
Whether you're a researcher, developer, or educator, DeduKt offers a flexible, extensible, and powerful tool set for advancing computational mathematics and science.

In the following section we would give an introduction to DeduKt as a project, we would explain driving philosophies in design, architecture, user-experience and development.
Later chapters would cover these topics in great detail and therefore, this introduction serves as an overview to the whole document.
