\section{Target Audience}\label{sec:target-audience}

DeduKt is designed with a specific set of users in mind: those who require symbolic computation and mathematical reasoning as part of their research or scientific work.
However, its capabilities and focus areas also determine the audiences it is not targeted towards.
Below is a breakdown of the primary users and those outside of the scope of DeduKt.

\subsection{Primary Target Audience}\label{subsec:primary-target-audience}

The primary target audience for DeduKt includes:

\begin{itemize}
    \item \textbf{Researchers and Academics in Mathematics and Physics}: DeduKt is ideally suited for researchers and students working in fields that rely on symbolic mathematics, such as algebra, calculus, differential equations, and other areas of pure and applied mathematics.
Its advanced symbolic reasoning capabilities and extensibility make it an excellent tool for conducting mathematical proofs, solving complex equations, and developing new mathematical theories.

    \item \textbf{Scientific Engineers and Data Analysts}: DeduKt bridges the gap between theoretical mathematics and real-world data analysis, making it a valuable tool for engineers and scientists who need to manipulate and reason with both symbolic and experimental data.
For example, researchers in computational physics, machine learning, or data science can use DeduKt to work with mathematical models while integrating experimental results into their workflows.

    \item \textbf{Open-Source and Community-Oriented Contributors}: DeduKt’s open-source nature and modular design make it an attractive platform for contributors who are interested in developing or enhancing symbolic computation libraries.
Researchers, software developers, and hobbyists who are passionate about advancing the state of open scientific software can contribute to DeduKt’s continued evolution.

    \item \textbf{Developers with an Interest in Symbolic Computation}: DeduKt is also suitable for software developers who are looking to integrate symbolic computation into their own applications.
The system’s extensibility and ability to define custom symbolic operations make it a useful resource for those building mathematical software or libraries.
\end{itemize}

\subsection{Secondary Target Audience}\label{subsec:secondary-target-audience}

The secondary target audience includes:

\begin{itemize}
    \item \textbf{Students in Computational Mathematics or Theoretical Physics}: DeduKt is a great tool for students learning computational techniques, symbolic manipulation, and mathematical modeling.
It can serve as both an educational tool and a research assistant for students in mathematics and physics programs.

    \item \textbf{Data Science and Machine Learning Enthusiasts}: While DeduKt is not designed as a full-fledged data science or machine learning platform, data scientists and ML practitioners who need symbolic computation for pre-processing, feature engineering, or model exploration will benefit from DeduKt’s capabilities to handle both theory and data in one platform.
\end{itemize}

\subsection{Not Targeted Audience}\label{subsec:not-targeted-audience}

DeduKt is not designed for the following audiences:

\begin{itemize}
    \item \textbf{General Software Developers}: While DeduKt allows for the extension of symbolic computation capabilities, it is not a general-purpose programming language like Kotlin, Go, or Python.
Developers seeking to build non-symbolic applications or software with no focus on mathematical reasoning or symbolic manipulation are not the primary users of DeduKt.

    \item \textbf{Users Seeking GUI-Based Software for Scientific Computing}: DeduKt is not focused on providing graphical interfaces for users.
While minimal interfaces may be provided for basic interaction, DeduKt’s core functionality is designed for script-based interaction and command-line execution.
Those who require full-fledged graphical user interfaces for interactive scientific computing will find other platforms, such as MATLAB or Mathematica, more suited to their needs.

    \item \textbf{Commercial Enterprises Requiring Dedicated Support}: DeduKt is an open-source software, and as such, it does not provide official commercial support or service-level agreements (SLAs).
Enterprises looking for a commercial product with dedicated support and guaranteed uptime should consider other options that cater specifically to enterprise needs.

    \item \textbf{Non-Mathematical Users or Casual Enthusiasts}: DeduKt is designed for advanced users dealing with mathematical reasoning and symbolic computation.
Casual users or individuals seeking software for basic tasks, such as word processing or general-purpose calculations, will not find DeduKt appropriate for their needs.

    \item \textbf{Advanced Machine Learning or AI Practitioners}: Although DeduKt may handle basic data manipulation tasks, it does not offer comprehensive tools for machine learning, neural networks, or advanced AI research.
Users interested in deep learning or complex machine learning pipelines will need to rely on specialized frameworks like TensorFlow or PyTorch.
\end{itemize}
